%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Joel}{Auterson}{\href{mailto:joel.auterson@gmail.com}{joel.auterson@gmail.com}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
Golang \textbullet{}   Java \textbullet{} C/C++/ObjC \textbullet{} C\# \\
JS/TypeScript \textbullet{} HTML/CSS \textbullet{} Protobuf \\
Shell, Python, Ruby, etc.
\sectionsep
\subsection{Technologies etc.}
AWS \textbullet{} Google Cloud \textbullet{} Kubernetes \\
Docker \textbullet{} Helm \textbullet{} Skaffold \\
Grafana/Prometheus \textbullet{} Elastic/Kibana \\
Terraform \textbullet{} PlayFab \\
iOS, Android, macOS, Linux \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Website:// \href{https://www.joelotter.com}{\bf{joelotter.com}} \\
GitHub:// \href{http://github.com/JoelOtter}{\bf{JoelOtter}} \\
Mastodon://  \href{https://otter.garden/@joel}{\bf{@joel@otter.garden}} \\
Bluesky://  \href{https://bsky.app/joelotter.com}{\bf{@joelotter.com}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Side Projects}
\subsection{Growl}
Portable 2D game engine written in\\modern C++.\\
\href{http://github.com/Bearwaves/growl}{\bf{github.com/Bearwaves/growl}}
\sectionsep
\subsection{eos4j}
Java library providing bindings to Epic\\Online Services.\\
\href{http://github.com/Bearwaves/eos4j}{\bf{github.com/Bearwaves/eos4j}}
\sectionsep
\subsection{Termloop}
A pure Go game engine for the terminal. Provides a renderloop and tools for making terminal-based games.\\
\href{http://github.com/JoelOtter/termloop}{\bf{github.com/JoelOtter/termloop}}
\sectionsep
\subsection{Kajero}
Interactive notebooks for the web,\\with clever graphing.\\
\href{http://github.com/JoelOtter/kajero}{\bf{github.com/JoelOtter/kajero}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.63\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{it me}
\sectionsep
I'm an experienced backend programmer, familiar with working in the cloud and at scale, and also have experience in programming games.
\sectionsep

\section{Experience}

\runsubsection{Emitwise}
\descript{| Senior Software Engineer}
\location{February 2022 - Present | London, UK}
\begin{tightemize}
\item Working on V2 of the Emitwise product, a platform to analyse and track carbon emissions and reductions.
\item Foundational work on infrastructure, application programming in Go and Typescript, instrumental in setting up engineering processes and pipelines.
\item Lots of Kubernetes, Helm, Terraform and AWS.
\end{tightemize}
\sectionsep

\runsubsection{Bearwaves}
\descript{| Programmer \& Producer}
\location{April 2016 - Present | London, UK}
\begin{tightemize}
\item Director of Bearwaves Ltd., a four-person game studio.
\item Programmer and producer roles on \href{https://store.steampowered.com/app/863400/Feud}{\bf{Feud}}, released in 2019 on Windows, macOS, Linux, iOS and Android.
\item Working on two more titles as well as \href{https://github.com/Bearwaves/growl}{\bf{Growl}}, a highly portable 2D game engine written in modern C++.
\end{tightemize}
\sectionsep

\runsubsection{Improbable}
\descript{| Software Engineer}
\location{September 2016 - January 2022 | London, UK}
\begin{tightemize}
\item Started working on WebTools team - working on full-stack web applications such as the Inspector. TypeScript, CSS \& Golang.
\item On Operate team, worked on various backend services and command line tools around authentication, account management and billing. Primarily Golang with some TypeScript.
\item On Worker team, worked on adding metrics to the core network layer of the SpatialOS SDK. Worked primarily with C/C++.
\item On Production team, worked with partner game studios to build authentication and inventory services. Golang, C\#, Docker, Kubernetes, Prometheus \& PostgreSQL.
\item Founding member of Online Services team. Helped to launch and scale Scavengers, a battle royale for PC and console.
\end{tightemize}
\sectionsep

\runsubsection{VMware}
\descript{| Software Engineering Intern}
\location{April 2015 – September 2015 | London, UK}
\begin{tightemize}
\item Worked on Hybrid DaaS team, building solutions for deploying and managing virtual desktops.
\end{tightemize}
\sectionsep

\runsubsection{MOO}
\descript{| Software Development Intern }
\location{July 2014 – September 2014 | London, UK}
\begin{tightemize}
\item Worked on the Digital Crew, maintaining a previous product and helping in the early development stages of a newer one.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\runsubsection{Imperial College London}
\descript{| MEng Computing}
\location{First-class Honours | September 2012 - June 2016}
\sectionsep{}

\end{minipage} 
\end{document}  \documentclass[]{article}

